### 2020-10-07 introduction.tex
new files for intro and conclusion
to discuss in the intro

\begin{document}
\section{Related Work and Conclusion}
\end{document}

>>>>

\begin{document}
\section{Introduction}

Things to discuss in the intro:

-- talking about what is GV and its "benefits"
-- next, talking about deadlock freedom property, the benefits and the fact that the original GVs do not satisfy DF
-- in the meantime, in a concurrent setting based on pi-calculus there is a curry-howard correspondence of logic and session typed pi, where DF holds
-- talk about CP here
-- \cite{dardha2018} brought the research fwd and added priorities a la Kobayashi and Padovani to CP, producing PCP
-- following that lead, we present PGV
-- running example of the scheduler in PGV (hopefully)
-- translation of PCP to PGV and what it means to have that.

a contribution paragraph with the following
-- PGV and what are the benefits
-- updated PCP
-- encoding PCP to PGV
-- technical results to be referred to explicitly

\end{document}
